Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex
[#1] Add probabilistic infrastructure to appendix
As requested by one of the referees, we've added an explicit
probability infrastructure to the beginning of the appendix.

Define the \sigmafield
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
$X_{nt}$. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays without modification to construct almost sure bounds on the
conditional moments $\Em$.

@@

Theorem~\ref{main-bootstrap-clt} implies that, for any fixed $\gamma$,
$W_n^{\prime *}(\gamma)$ is asymptotically normal and, as a
partial sum of an \mds, $W_n^{\prime *}$ has asymptotically independent
increments. To see this, choose $\gamma, \gamma' \in [0,1]$ and
$\delta, \delta' > 0$ so that $\delta + \gamma \leq \gamma'$. Since
the increments of $W_n^{\prime *}$ are uncorrelated conditional on
$X_{1n},\dots,X_{nn}$, and $\Ms$, we have
\begin{equation*}
    \E\big| (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big| = 0
\end{equation*}
for large enough $n$ if $\gamma' > \gamma + \delta$. If $\gamma' =
\gamma + \delta$ then
\begin{multline*}
  \E\big[(W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = \\
  \E \Em^*\big\{- Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\}.
\end{multline*}
But this second quantity can be bounded:
\begin{align*}
  \E \Em^*\big\{-& Z_n^*(\lfloor \gamma' n \rfloor,
  K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\} \\
  &\leq \big\{\E \Em\big[Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)\big]^2 \\
  & \quad \times \big\{\E \Em Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))^2\big\}^{1/2} \\
  &\leq C \E M_{n, \lfloor (\gamma + \delta) J_n \rfloor} / n
\end{align*}
for some constant $C$ by
Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
converges to zero by Lemma~\ref{block-length-convergence-lemma}.

@@

\begin{lem}\label{equivalent-convergence-from-lie-lemma}
  If $\{A_n\}$ is a sequence of events then the following are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}

>>>>

First, the relevant probability infrastructure.  Let
$(S, \Omega, \pr)$ be a probability space and define the sequence of
sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
that designate the start period of each bootstrap ``block.'' Also
define the \sigmafield\ generated by the stationary bootstrap's block
lengths alone, which will be used repeatedly in our results,
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$'s, $V_{nt}$'s, and
$u_{nj}$'s, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
other random variables. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays with only small modifications to construct almost sure bounds on the
conditional moments $\Em$.

@@

Theorem~\ref{main-bootstrap-clt} implies that, for any fixed $\gamma$,
$W_n^{\prime *}(\gamma)$ is asymptotically normal and, as a
partial sum of an \mds, $W_n^{\prime *}$ has asymptotically independent
increments. To see this, choose $\gamma, \gamma' \in [0,1]$ and
$\delta, \delta' > 0$ so that $\delta + \gamma \leq \gamma'$. Since
the increments of $W_n^{\prime *}$ are uncorrelated conditional on
$X_{1n},\dots,X_{nn}$, and $\Ms$, we have
\begin{equation*}
    \E\big[ (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = 0
\end{equation*}
for large enough $n$ if $\gamma' > \gamma + \delta$. If $\gamma' =
\gamma + \delta$ then
\begin{multline*}
  \E\big[(W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = \\
  \E \Em^*\big\{- Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\}.
\end{multline*}
But this second quantity can be bounded:
\begin{align*}
  \E \Em^*\big\{-& Z_n^*(\lfloor \gamma' n \rfloor,
  K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\} \\
  &\leq \big\{\E \Em\big[Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)\big]^2 \\
  & \quad \times \big\{\E \Em Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))^2\big\}^{1/2} \\
  &\leq C \E M_{n, \lfloor (\gamma + \delta) J_n \rfloor} / n
\end{align*}
for some constant $C$ by
Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
converges to zero by Lemma~\ref{block-length-convergence-lemma}.

@@

\begin{lem}\label{equivalent-convergence-from-lie-lemma}
  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
  are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}
